---
output:
  html_document: default
  pdf_document: default
---

The study that we're going to do corresponds to the "One Way Analysis of Variance (ANOVA)". We're actually trying to see if the dose of a sweetener increases the weights of piglets i.e. makes them fat. In this regard, one experiment was performed.
A set of piglets with similar conditions where selected and 5 different sweetener doses where
considered and randomly assigned to the piglets. The response variable is the mean weight
gained per day, GMD, and the explanatory variable is the sweetener dose. Here, as you can guess, the sweetner dose is a **categorical variable**.

```{r reading_data}
dd<-read.csv2("GMD.csv")
library(car)
library(lsmeans)
library(tables)
library("RcmdrMisc")
library("multcompView")
```
View(dd)

We can check if the categorical variable is a factor or not. In case, it is not a factor which is a pre-requisite condition for performing the ANOVA test, we can actually convert it into a factir variable and proceed. The following code accomplishes this task.
```{r checking_factor_variable}
if(is.factor(dd$DOSI)==F){
  dd$DOSI<-as.factor(dd$DOSI)
}else{
  cat("The variable is a factor. You can proceed with the analysis")
}
```

Creating a table of the mean and standard deviation with respect to the categorical variable "DOSI" that corresponds to the different dosage of the sweetner.

```{r creating_table_of_mean_and_sd}
tabular(DOSI~Y*((n=1)+mean+sd),dd)
```


```{r}
with(dd, plotMeans(Y, DOSI, error.bars="conf.int",level=0.95, connect=TRUE))

mod<-lm(Y~DOSI,dd)

summary(mod)

anova(mod)
Anova(mod,ty=3)
lsm<-lsmeans(mod,~DOSI)
lsm
pairs(lsm)
cld(lsm,alpha=0.01)
plot(lsm,level=0.99)
confint(lsm,level=0.99)

plot(predict(mod),resid(mod))
abline(h=0,lty=2)

plot(rstudent(mod))
abline(h=c(-2,0,2),lty=2)

plot(mod,ask=F)

predict(mod)
resid(mod)
hatvalues(mod)
dffits(mod)

leveneTest(mod)
leveneTest(Y~DOSI,dd)
```

### Performing the Bartlett's Test
**Bartlett's test**:
Bartlett's test allows you to compare the variance of two or more samples to determine whether they are drawn from populations with equal variance. It is suitable for normally distributed data. The test has the null hypothesis that the variances are equal and the alterntive hypothesis that they are not equal [1].

This test is useful for checking the assumptions of an analysis of variance. Suppose you want to use Bartlett's test to determine whether the the variance in Weight (Y) is the same for all sweetner groups (DOSI). A **significance level of 0.05** will be used.
```{r}
bartlett.test(Y~DOSI,dd)
```
From the output we can see that the p-value of 0.7125 is not less than the significance level of 0.05. This means **we cannot reject the null hypothesis** that the **variance is the same for all sweetner groups**. This means that there is no evidence to suggest that the variance in sweetner dosages is different for the treatment groups.


### Tukey's Test
Tukey test on all possible pairs
```{r}
aov_sweetner<-aov(formula = Y~DOSI, data = dd)
TukeyHSD(aov_sweetner, conf.level=.95)
```


References:

[1] Montgomery, D.C. and Runger, G.C., 2007. Applied Statistics and Probability for Engineers, 4th ed. John Wiley & Sons.
