---
output:
  html_document: default
  pdf_document: default
---

Loading the relevant packages:
```{r}
library(readr)
sub_data <- read_delim("~/Linear Models/sub_data.txt", 
    "\t", escape_double = FALSE, trim_ws = TRUE)
View(sub_data)


library(lsmeans)
library(car)
```

### Question 1
Define the linear model that explains FS based on SHIDR: We are trying to fit the model FS~SHIDR.  

**a) Fit the model and perform the diagnostics.**

```{r linear_model}
data<-as.data.frame(sub_data)
lin_mod<-lm(formula = FS~SHIDR, data = sub_data)

```

We can see the summary of the model by performing the following command-
```{r summary_lin_mod}
summary(lin_mod)

(summary(lin_mod)$sigma)**2

```



```{r}
par(mfrow=c(2,2))
plot(lin_mod)
```

**  b) Define and perform the ANOVA test.**
Now, performing the
```{r}
anova_lin_mod<-anova(lin_mod)
anova_lin_mod
```

* c)  Compare the four treatments using Tukey's method.
```{r}

# Performing the ANOVA test
anova(lin_mod)

# ANOVA type 3 test
Anova(lin_mod,ty=3)
lsm<-lsmeans(lin_mod,~SHIDR)
lsm

# Pairwise comparisons
pairs(lsm)

```

We can express the results of the Tukey's Test using the ***Compact letter display of pairwise comparisons*** of the four various levels of SHIDR. 

Further, we can plot the results of the four levels of SHIDR and their 

```{r}
cld(lsm,alpha=0.01)

```

```{r}
# Plotting the lsmean versus four levels of factor SHIDR
plot(lsm,level=0.99)
```
The confidence interval used here has the confidence level of 0.01. The parameter **alpha** can be used to pass the value of desired significance level **0.01**. 


```{r}
# Confidence Interval
confint(lsm,level=0.99)
```


